---
title: "Vijay's Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation : rows
    vertical_layout: fill
    social : ["twitter","facebook","menu"]
    source_code: embed
  
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(ggvis)
```


```{r }
data<-read.csv("c:/Users/Vijay/Desktop/POM-681/Data/airline.csv")
data<- data %>% filter(! is.na(DepDelay), ! is.na(DepDelayMinutes))
data1<- data %>% filter(!is.na(ArrDelay))
```


```{r }
mycolors<-c("blue","#ffc125","darkgreen","darkorange")
```


Interactive Data visualization
===============================================================================================================

Row
---------------------------------------------------------------------------------------------------------------

###  flight Delay Analysis

```{r }
valueBox(paste("Delay"),
         color="warning")

```


### Flight Delay in US

```{r }
valueBox(length(data$OriginState),
         icon = "fa-user")

```

### **Departure Delay**

```{r }
gauge(round(mean(data$DepDelay),
          digits=2),
      min =  0,
      max= 60,
      gaugeSectors(success = c(0,15),
                   warning = c(15,30),
                   danger = c(30,60),
                   colors = c("green","yellow","red")))

```

### Massachusetts

```{r }
valueBox(mean(data$DepDelayMinutes[data$DestState == "MA"]),
         icon = 'fa-buiding')
```

### New Hampshire

```{r}
valueBox(mean(data$DepDelayMinutes[data$DestState == "NH"]),

         icon = 'fa-buiding')
```

### Texas

```{r}
valueBox(mean(data$DepDelayMinutes[data$DestState == "TX"]),
         icon = 'fa-buiding')
```

### Rhode Island

```{r}
valueBox(mean(data$DepDelayMinutes[data$DestState == "RI"]),
         icon = 'fa-buiding')
```

Row
---------------------------------------------------------------------

### Departure Delay By Origin State

```{r}
p1 <- data %>%
  group_by(OriginState) %>%
  summarise(DepDelay =n()) %>%
  plot_ly (x = ~ OriginState,
          y = ~ DepDelay,
          color ="blue",
          type = 'bar') %>%
layout(xaxis = list(title = "Departure Delay by Origin State"),
yaxis = list(title = 'Count'))
p1
  
```
### Top States Arrival Delay

```{r}
p2 <- data1 %>%
  group_by(DestState) %>%
  summarise(ArrDelay =n()) %>%
  filter(ArrDelay>1000) %>%
  plot_ly (labels = ~ DestState,
          values = ~ ArrDelay,
          marker = list(color = mycolors)) %>%
  add_pie(hole = 0.3) %>%
  layout(xaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F),
         yaxis = list(zeroline = F,
                      showline = F,
                      showticklabels=F,
                      showgrid=F))
p2
```
### Day of Month vs Departure Delay

```{r}
p3 <- plot_ly(data,
               x = ~DayofMonth,
               y = ~DepDelay,
               text = paste("DayofMonth", data$DayofMonth,
                            "DepDelay", 
                            data$DepDelay),
                            type = "bar")%>%
                 layout(xaxis = list(title ="DayofMonth "),
                      yaxis = list(Title = "DepDelay"))
p3
```

Row
-----------------------------------------------------------------------------------------------------------

### Scatter plot Day of Week Vs Arrival Delay
```{r}
p4 <- plot_ly(data1, x=~ DayOfWeek) %>%
  add_markers(y = ~ ArrDelay,
              text = ~paste("ArrDelay:",ArrDelay),
              showlegend = F)%>%
  add_lines(y= ~ fitted (loess(ArrDelay ~ DayOfWeek)),
            name = "Loess Smoother",
            color = I("#FFC125"),
            showlegend = T,
            Line = list(width=5)) %>%
  layout(xaxis = list(title = " Day of week"),
         yaxis = list(title = "Arrival Delay"))
p4
```

###  Arrival Delay Vs Unique Carrier

```{r}

plot_ly(data1, x = data1$UniqueCarrier, y= data1$ArrDelay, text = paste("Destination State:", data1$DestState), mode = "markers", color = data1$DestState) %>%
  layout(title = ' Arrival delay Vs Unique Carrier',
         xaxis = list(title = 'Unique Carrier',
                      zeroline = TRUE),
         yaxis = list(title = 'Arrival delay (mins)'))

```


Map
=====================================================================================

### Map
```{r}
air <- data %>%
  group_by(OriginStateName)%>%
  summarize(total = n())
OriginStateName <- abbr2state(air$OriginStateName)

highchart() %>%
  hc_title(text = "Origin state in US") %>%
  hc_subtitle(text = "Source: airline.csv") %>%
  hc_add_series_map(usgeojson, air,
                    name = "Origin airport",
                    value = "total",
                    joinBy = c("woename", "OriginStateName")) %>%
  hc_mapNavigation(enabled = T)


```

Data Table
====================================================================================

```{r}
datatable(data,
          caption = "Delay Data",
          rownames = T,
          filter = "top",
          options = list(pageLength = 25))

```

Interactive Pivot table
=====================================================================================================================


```{r}
rpivotTable(data,aggregatorName = "Count",
            cols="ArrDelay",
            rows="OriginState",
            rendererName = "Heatmap")

```

Summary {data-orientation=columns}
=============================================================================================================


column
------------------------------------------------------------------------------------------------------------

### Max Arrival Delay 

```{r}
valueBox(max(data1$ArrDelay),
         icon="fa-user")

```

### Average Arrival delay

```{r}

valueBox(round(mean(data1$ArrDelay),
               digits = 2),
         icon="fa-area-chart")

```

### Average Departure delay

```{r}

valueBox(round(mean(data$DepDelay),
               digits = 2),
         icon="fa-area-chart")

```

### Average Carrier Delay
```{r}
data<- data %>% filter(! is.na(CarrierDelay))
valueBox(round(mean(data$CarrierDelay),
               digits = 2),
         icon="fa-area-chart")

```

### Average Weather Delay
```{r}
data<- data %>% filter(! is.na(WeatherDelay))
valueBox(round(mean(data$WeatherDelay),
               digits = 2),
         icon="fa-area-chart")

```

### Average NASDelay

```{r}
data<- data %>% filter(! is.na(NASDelay))
valueBox(round(mean(data$NASDelay),
               digits = 2),
         icon="fa-area-chart")

```

### Average Securuty Delay

```{r}
data<- data %>% filter(! is.na(SecurityDelay))
valueBox(round(mean(data$SecurityDelay),
               digits = 2),
         icon="fa-area-chart")

```

### Average Late Aircraft Delay

```{r}
data<- data %>% filter(! is.na(LateAircraftDelay))
valueBox(round(mean(data$LateAircraftDelay),
               digits = 2),
         icon="fa-area-chart")

```

Column
------------------------------------------------------------------------------------------------------------------

Report

* This is a report on `r length(data1$ArrDelay)` airline Delay.

* The average Arrival Delay was `r mean(data1$ArrDelay)`.

* The average  Carrier Delay was `r mean(data$CarrierDelay)`.

* The  average weather Delay was `r mean(data$WeatherDelay)`.

* The average NAS Delay was `r mean(data$NASDelay)`.

* The average Security Delay was `r mean(data$SecurityDelay)`.

* The average Late aircraft Delay was `r mean(data$LateAircraftDelay)`.

This report was generated on `r format(Sys.Date(), format = "%B %d, %Y")`.

About Report
===================================================================================================================

Work : Project-1, POM-681

Topic : Development of Dashboard

Data : airline.csv

Created by : Vijay Kumar Singh Kshetri

Confidential: HIGHLY!


